A Constraint Solving Approach to Parikh Images of Regular Languages

### 2023-07-11 calculus.tex
bw-reach

\begin{definition}\label{def:connected} $\Connected(\Automaton, \Filter)$
  holds for some automaton $\Automaton = \AutomatonTuple$ and
  transition selection function
  $\Filter:\: \Transitions \to \Naturals$
  if for every
  $\Transition = \FromLabelTo{\State}{}{\State'} \in \Transitions$,
  if $\Filter(\Transition) > 0$ then there is some $\Filter$-selected
  path that reaches $\Transition$'s starting state~$\State$. More formally,
  if $\Filter(\Transition) > 0$ then there is some
  path~$\Path \in \Paths(\Automaton)$ with
  $\Filter(\Transition') > 0$ for every $\Transition' \in p$, and $\State \in
  \StatesOf(p)$. Predicate~$\Connected(\Automaton, \Filter)$ represents the
  condition that $\Automaton$ is connected with respect to the selection
  function $\Filter$ for every transition, and is implied by
  $\SinglePredicateInstance$.
\end{definition}

>>>>

\begin{definition}\label{def:connected} $\Connected(\Automaton, \Filter)$
  holds for some automaton $\Automaton = \AutomatonTuple$ and
  transition selection function
  $\Filter:\: \Transitions \to \Naturals$
  if for every
  $\Transition = \FromLabelTo{\State}{}{\State'} \in \Transitions$,
  if $\Filter(\Transition) > 0$ then there is some $\Filter$-selected
  accepting path that visits $\Transition$'s starting state~$\State$. More formally,
  if $\Filter(\Transition) > 0$ then there is some
  path~$\Path \in \Paths(\Automaton)$ with
  $\Filter(\Transition') > 0$ for every $\Transition' \in p$, and $\State \in
  \StatesOf(p)$ such that $p$ ends in an accepting state $\State' \in \AcceptingStates$. The predicate~$\Connected(\Automaton, \Filter)$ represents the
  condition that $\Automaton$ is connected under the selection
  function $\Filter$ for every transition, and is implied by
  $\SinglePredicateInstance$.
\end{definition}
